Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-12 manuscript/manuscript.Rmd
finished 1d section, starting 3d

@@

Part of what makes eq. \eqref{eq:may} an interesting study case is the presence of a *tipping point*.

>>>>

## Single species models

@@

Part of what makes eq. \eqref{eq:may} an interesting study case is the presence of a *tipping point* (see Fig. \ref{tbd}).
Holding the value of $\beta$ fixed, for intermediate values of $H$ there exist two stable fixed points for the state $V_1$ of the system, these two attractors separated by an unstable fixed point.
At a certain threshold value of $H$, however, the top stable fixed point collides with the unstable fixed point and both are annihilated.
For this value of $H$, and for higher values, only the lower fixed point remains.

This structure implies two things.
First, that a drift in $H$ could lead to catastrophic consequences, with the population $V_1$ plummeting to the lower fixed stable point.
Second, that if the evolution of $V_1$ is *stochastic*, then, even at values of $H$ below the threshold point, the system runs a sizeable danger of tipping over towards the lower stable point.

## A three species model
